---
title: "Investigators"
---

<style>
.flex-grid-thirds {
    display: flex;
    flex-flow: row wrap;
    align-content: center;
}

.flex-grid-thirds .col {
    width: 33%;
    margin-top: 0px;
    margin-bottom: 0px;
}

@media (max-width: 400px) {
    .flex-grid-thirds {
        display: block;
        .col {
            width: 100%;
            margin = 0 0 10px 0;
        }
    }
}

* {
    box-sizing: border-box;
}
.col {
    padding: 10px;
    border-style: solid;
    border-spacing: 20px;
    border-color: #cbd1cc;
    border-width: thin;
}

.more--button {
    color: #3a3a3a;
    border-color: #3a3a3a;
    border-style: solid;
    background-color: transparent;
    border-width: 1px;
    padding: 5px 5px 5px 5px;
    display: flex;
    justify-content: center;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, results='asis', layout = "l-body-outset"}
cat(":::: flex-grid-thirds \n")
for (member in staff_list) {
    condensr::generate_markdown_for_member(member)
}
cat("::::")
```
